Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-07 MUSES_vs_BYOD_solutions.tex
Adding clarification about MUSES advantages with respect to self-adaptation

As in the client, we describe the three main components:
\begin{itemize}
	 \item \textit{System Database}: it stores all the information that the system can manage, including authentication data, enterprise security policies, values of the assets, 
% Antonio - no sé qué expresión será más correcta, pero deberíamos poner siempre "values of the assets" o "values of the assets". Yo me inclino por la segunda.
user-related information (trust, context), events data, and, of course, security rules to apply (with regard to the security policies).

	 \item \textit{Continuous Real-Time Event Processor (MusCRTEP)}: this component is the core of the MUSES system with respect to the decision making process. It includes an \textit{Event Processor}, the module in charge of performing the event correlation process \cite{deliverable21, deliverable52}. This is done by a so-called `Event correlation engine', which is in charge of taking the user action events that are sent from the device client, and analysing them to look for an existing security rule that could be applied to the situation. The engine discovers that by analysing the context events which are sent with the user action event, so that a complete model of the risks can be built. The output of this module is an `access request' which is sent to the \textit{RT2AE}. It considers the information included in the access request, as well as other information such as trust data and profiles, values of the assetss, s
% Antonio - "values of the assets"
user reputation, or opportunity, to perform a risk and trust analysis task \cite{RT2AE_SOTICS13}. Finally, the RT2AE extracts the set of potential rules to consider in the analysed situation, and these rules are therefore transformed into decisions (or Device Policies) and submitted to those devices to which they apply.

@@

MUSES is mainly a free, open-source, platform independent solution, and that makes it a very good option in a first comparison against most of the proprietary, close and system-specific tools presented in Section \ref{sec:toolsreview} (all but WSO2). In addition, most of the existing tools take into account only smartphones and tablets, but MUSES also  covers laptops and company PCs too, thus, it is not only for BYOD. Moreover, the companies which might want to work with one of the reviewed systems need a specific operating system in the server (such as Windows Server, for instance), being even more restrictive in some cases. This is specially remarkable in the case of the Blackphone, forcing the companies and the employees to purchase a specific device. MUSES is a good solution towards these cases, since it is a multiplatform system in both the client and the server.

Another comparison would be that the existing products are mostly policy-based, while MUSES makes its decisions not only considering policies, but also based on the terminals and users context (connection properties, or trust value of the device, for instance), to really understand the real risk that comes with a specific action.

Also related to this issue, a very big plus of the MUSES system (not present in the other solutions) is its self-adaptivity power. Thus, MUSES is able to adapt to changes, either regarding corporate security policies, newly discovered vulnerabilities or threats, different environments of use, or user profiles.

Moreover, another clear advantage over the rest is that MUSES can work in both online and offline modes, depending on the client being able to connect with the server or not, which favours a real-time decision making process.

>>>>

As in the client, we describe the three main components:
\begin{itemize}
	 \item \textit{System Database}: it stores all the information that the system can manage, including authentication data, enterprise security policies, values of the assets, 
% Antonio - no sé qué expresión será más correcta, pero deberíamos poner siempre "assets' values" o "values of the assets". Yo me inclino por la segunda.
user-related information (trust, context), events data, and, of course, security rules to apply (with regard to the security policies).

	 \item \textit{Continuous Real-Time Event Processor (MusCRTEP)}: this component is the core of the MUSES system with respect to the decision making process. It includes an \textit{Event Processor}, the module in charge of performing the event correlation process \cite{deliverable21, deliverable52}. This is done by a so-called `Event correlation engine', which is in charge of taking the user action events that are sent from the device client, and analysing them to look for an existing security rule that could be applied to the situation. The engine discovers that by analysing the context events which are sent with the user action event, so that a complete model of the risks can be built. The output of this module is an `access request' which is sent to the \textit{RT2AE}. It considers the information included in the access request, as well as other information such as trust data and profiles, values of the assets, 
% Antonio - "values of the assets"
user reputation, or opportunity, to perform a risk and trust analysis task \cite{RT2AE_SOTICS13}. Finally, the RT2AE extracts the set of potential rules to consider in the analysed situation, and these rules are therefore transformed into decisions (or Device Policies) and submitted to those devices to which they apply.

@@

MUSES is mainly a free, open-source, platform independent solution, and adopts the recommended best practices by Romer \cite{Romer14BestPractices}. %Está bien aquí Fergu?
 These features make it a good alternative to most of the proprietary, close and system-specific tools presented in Section \ref{sec:toolsreview} (all but WSO2). In addition, most of the existing tools take into account only smartphones and tablets, but MUSES also covers laptops and company PCs, thus, it is not only for BYOD. Moreover, the companies which might want to work with one of the reviewed systems need a specific operating system in the server (such as Windows Server, for instance), being even more restrictive in some cases. This is specially remarkable in the case of the Blackphone, forcing the companies and the employees to purchase a specific device. MUSES is a good solution towards these cases, since it is a multiplatform system in both the client and the server.

Another comparison would be that the existing products are mostly policy-based, while MUSES makes its decisions not only considering policies, but also based on the terminals and users context. Thus it uses connection properties, or the device trust value, for instance, to really understand the real risk that comes with a specific action.

Also related to this issue, a very big advantage of the MUSES system that is not present in the other solutions is its self-adaptivity power. The proposed system uses different methods to create new security rules, being their aim to cover new vulnerabilities or threats. Thus, MUSES is able to adapt to changes by applying classification techniques to create new rules, and then refining the whole set of existing policies. Additionally, MUSES is able to discover new threats by a combination of real-time risk and trust analysis, plus a classifier trained with all the occurred events in the system.

Moreover, another clear improvement over the rest is that MUSES can work in both online and offline modes, depending on the client being able to connect with the server or not, which favours a real-time decision making process.
